disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
Not quite sure. The full sentence on our papers seemed ott. Saying it was developed in eco but is now important, not just in methods papers, in epi, works well... maybe.

Methods for estimating high-resolution risk maps from aggregated response data over large spatial regions are 
becoming increasingly sought after in disease risk mapping~\cite{li2012log, diggle2013spatial, wilson2017pointless}, especially in malaria mapping~\cite{sturrock2014fine, sturrock2016mapping}. 
and ecological species distribution~\cite{keil2013downscaling, barwell2014can}. The aggregation of response data over large 
heterogenous regions is problematic for understanding the fine-scale distribution. However, by using fine-scale information from related covariates we can inform the hetrogeneity of the response variable of interest within the agreggated area. This method has recently been applied in the latest global high-resolution maps of \emph{Plasmodium falciparum} and \emph{Plasmodium vivax} malaria~\cite{falciparum2019, vivax2019}.

>>>>

Methods for estimating high-resolution risk maps from aggregated response data over large spatial regions are 
becoming increasingly sought after in disease risk mapping~\cite{li2012log, diggle2013spatial, wilson2017pointless}, especially in malaria mapping~\cite{sturrock2014fine, sturrock2016mapping}. 
Disaggregation regression, was first applied to ecological species distribution modelling~\cite{keil2013downscaling, barwell2014can} but has now become an important method in disease risk mapping \cite{falciparum2019, vivax2019}. 
The aggregation of response data over large heterogenous regions is problematic for understanding the fine-scale distribution. However, by using fine-scale information from related covariates we can inform the hetrogeneity of the response variable of interest within the agreggated area.
